GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-10-16 ennv.tex
update

\begin{itemize}
\item ReLU (Rectified Linear Unit): ReLU is the most popular activation function in DNNs. It returns 0 if the input is less than zero, and the input itself otherwise. It is often used in hidden layers and skipped in the output layer.  
A ReLU activated neuron is said to be \emph{active} if its input value is greater than
zero and \emph{inactive} otherwise.\\
    \begin{center}
        $ReLU(x) = \max(x,0)$
    \end{center}

@@

\chapter{Search Algorithms}
\autoref{fig:alg} shows \dd{}, a reference architecture~\cite{nakagawa2014consolidating} 
for modern DNN verifiers that we use to illustrate our observations.  
\dd{} takes as input a ReLU-based DNN $\mathcal{N}$ and a formulae $\phi_{in}\Rightarrow \phi_{out}$ representing the property of interest.

>>>>

\begin{itemize}
\item ReLU (Rectified Linear Unit):  ReLU returns 0 if the input is less than zero, and the input itself otherwise. 
A ReLU activated neuron is said to be \emph{active} if its input value is greater than zero and \emph{inactive} otherwise.
ReLU is the most popular activation function in DNNs.\\
    \begin{center}
        $ReLU(x) = \max(x,0)$
    \end{center}

@@

\chapter{Search Algorithms}

\begin{algorithm}[t]
    \SetKwFor{Parfor}{parfor}{do}{endparfor}

    \SetKwInOut{Input}{input}
    \SetKwInOut{Output}{output}

    \SetKw{Break}{break}
    \SetKw{Continue}{continue}
    \SetKw{In}{in}

    \SetKwData{model}{model}
    \SetKwData{layer}{layer}
    \SetKwData{nextlayer}{layer$_{i+1}$}
    \SetKwData{prooftree}{proof}
    \SetKwData{leaf}{node}
    \SetKwData{status}{status}
    \SetKwData{minimum}{objval}
    \SetKwData{mynull}{null}

    \SetKwFunction{InputMILP}{AddInputConstrs}
    \SetKwFunction{GetUnstableNeurons}{GetUnstableNeurons}
    \SetKwFunction{PiecewiseLinearMILP}{AddConstrsPWL}
    \SetKwFunction{LinearMILP}{AddConstrsLinear}
    \SetKwFunction{Maximize}{Maximize}
    \SetKwFunction{Minimize}{Minimize}
    \SetKwFunction{Feasible}{CheckFeasibility}
    \SetKwFunction{Optimize}{Optimize}
    \SetKwFunction{isPiecewiseLinear}{isPiecewiseLinear}
    \SetKwFunction{CreateStabilizedMILP}{CreateStabilizedMILP}
    \SetKwFunction{GetLeafNodes}{GetLeafNodes}
    \SetKwFunction{AddConstrs}{AddConstrs}
    \SetKwFunction{RemoveConstrs}{RemoveConstrs}
    \SetKwFunction{AddObjective}{AddObjectives}
    \SetKwFunction{ShortenSplitConstrs}{ShortenSplitConstrs}
    \SetKwFunction{RemoveLeafNodes}{RemoveLeaves}
    \SetKwFunction{StoppingConditions}{StoppingConditions}
    \SetKwFunction{RepOK}{RepOK}
    \SetKwFunction{RaiseError}{RaiseError}

    \SetKwInOut{Input}{input}
    \SetKwInOut{Output}{output}
    \SetKw{Break}{break}
    \SetKw{Continue}{continue}
    \SetKwFunction{Backtrack}{Backtrack}
    \SetKwFunction{Select}{Select}
    \SetKwFunction{Decide}{Decide}
    \SetKwFunction{BCP}{BCP}
    \SetKwFunction{Deduce}{Deduce}
    \SetKwFunction{AnalyzeConflict}{AnalyzeConflict}
    \SetKwFunction{BooleanAbstraction}{BooleanAbstraction}
    \SetKwFunction{AddClause}{AddClause}
    \SetKwFunction{isTotal}{isTotal}
    \SetKwFunction{randomattack}{RandomAttack}
    \SetKwFunction{pgd}{PGDAttack}

    \SetKwFunction{DPLLT}{DPLLT}
    \SetKwFunction{isValid}{isValid}
    \SetKwFunction{isEmpty}{isEmpty}
    \SetKwFunction{LPSolver}{LPSolver}
    \SetKwFunction{Solve}{Solve}
    \SetKwFunction{FindLayerNodes}{FindLayerNodes}
    \SetKwFunction{TightenInputBounds}{TightenInputBounds}
    \SetKwFunction{Abstract}{Abstract}
    \SetKwFunction{Check}{Check}
    \SetKwFunction{Decide}{Decide}
    \SetKwFunction{Imply}{Imply}
    \SetKwFunction{Lower}{LowerBound}
    \SetKwFunction{Upper}{UpperBound}
    \SetKwFunction{GetInputBounds}{GetInputBounds}
    \SetKwFunction{GetInputs}{GetInputs}
    \SetKwFunction{GetNumInputs}{GetNumInputs}
    \SetKwFunction{CurrentConflictClause}{CurrentConflictClause}
    \SetKwFunction{StopCriterion}{StopCriterion}
    \SetKwFunction{LastAssignedLiteral}{LastLiteral}
    \SetKwFunction{LiteralToVariable}{LiteralToVariable}
    \SetKwFunction{Antecedent}{Antecedent}
    \SetKwFunction{BinRes}{BinRes}
    \SetKwFunction{BacktrackLevel}{BacktrackLevel}
    \SetKwFunction{AddClause}{AddClause}
    \SetKwFunction{ActivationStatus}{ActivationStatus}
    \SetKwFunction{Backjump}{Backjump}
    \SetKwFunction{EstimateBounds}{EstimateBounds}

    \SetKwData{problems}{ActPatterns}
    \SetKwData{implicationgraph}{igraph}
    \SetKwData{literal}{lit}
    \SetKwData{variable}{var}
    \SetKwData{antecedent}{ante}
    \SetKwData{conflict}{conflict}
    \SetKwData{none}{none}
    \SetKwData{layerid}{lid}
    \SetKwData{hiddenbounds}{hidden\_bounds}
    \SetKwData{layerbounds}{layer\_bounds}
    \SetKwData{inputs}{inputs}
    \SetKwData{inputbounds}{input\_bounds}
    \SetKwData{outputbounds}{output\_bounds}
    \SetKwData{infeasible}{INFEASIBLE}
    \SetKwData{unreachable}{UNREACHABLE}
    \SetKwData{maxinputs}{MAX\_NUM\_INPUT}
    \SetKwData{assignment}{$\sigma$}
    \SetKwData{dl}{dl}
    \SetKwData{lpmodel}{solver}
    \SetKwData{clauses}{clauses}
    \SetKwData{conflict}{conflict}
    \SetKwData{clause}{clause}
    \SetKwData{igraph}{igraph}
    \SetKwData{cex}{cex}
    \SetKwData{sat}{sat}
    \SetKwData{unsat}{unsat}
    \SetKwData{certified}{certified}
    \SetKwData{uncertified}{uncertified}
    \SetKwData{submodel}{sub\_model}

    \SetKwData{true}{true}
    \SetKwData{false}{false}
    \DontPrintSemicolon

    \SetKwFunction{Restart}{Restart}

    \SetKwData{counterexample}{cex}
    \SetKwData{conflictclause}{conflict\_clause}
    \SetKwData{isconflict}{is\_conflict}

    \footnotesize
    \DontPrintSemicolon

    \Input{DNN $\mathcal{N}$, property $\phi_{in} \Rightarrow \phi_{out}$}
    Output{($\unsat, \prooftree$)}
    \Output{($\unsat, \prooftree$) if property is valid, otherwise ($\sat, \counterexample$)}
    \BlankLine

    $\problems \leftarrow \{ \emptyset \}$ \tcp{initialize verification problems} 
    $\prooftree \gets \{ ~ \}$ \tcp{initialize proof tree}\label{line:prooftree}

    \While(\tcp*[h]{main loop}){$\problems$}{\label{line:dpllstart}
        % \tcp{$\sigma_i$ is the activation pattern of problem $i$-th}
        $\sigma_i \gets \Select(\problems)$ \tcp{process problem $i$-th}
        % \Parfor(\tcp*[h]{process in parallel}){$\sigma_i ~\In~ \problems$}{ \label{line:parfor}
            \If{\Deduce{$\mathcal{N}, \phi_{in}, \phi_{out}, \sigma_i$}}{\label{line:deduce}
                $(\counterexample, v_i) \leftarrow \Decide(\mathcal{N}, \phi_{in}, \phi_{out}, \sigma_i)$ \\ \label{line:decide}
                \If(\tcp*[h]{found a valid counter-example}){$\counterexample$}{
                    \Return{$(\sat, \counterexample)$} 
                }
                \tcp{create new activation patterns}
                $\problems \leftarrow \problems \cup \{ \sigma_i \land v_i ~;~ \sigma_i \land \overline{v_i} \}$ \;
            }
            \Else(\tcp*[h]{detect a conflict}){
                % $\clauses \leftarrow \clauses \cup \AnalyzeConflict(\igraph_i)$ \\ \label{line:analyze_conflict}
                $\prooftree \leftarrow \prooftree \cup \{ \sigma_i \}$ \tcp{build proof tree} \label{line:record_proof}
            }
        % }
        % \If(\tcp*[h]{no more problems}){$\isEmpty(\problems)$}{
        % }

    }\label{line:dpllend}
    \Return{$(\unsat, \prooftree)$}

    \caption{The \dd{} algorithm with proof generation.}\label{fig:alg}
\end{algorithm}

\autoref{fig:alg} shows \dd{}, a reference architecture~\cite{nakagawa2014consolidating} 
for modern DNN verifiers that we use to illustrate our observations.  
\dd{} takes as input a ReLU-based DNN $\mathcal{N}$ and a formulae $\phi_{in}\Rightarrow \phi_{out}$ representing the property of interest.
